% !TEX root = ../main.tex

%----------------------------------------------------------------------------------------
% ABSTRACT PAGE
%----------------------------------------------------------------------------------------
%\begin{abstract}
%\addchaptertocentry{Abstract} % Add the abstract to the table of contents
%The abstract is like a miniature version of the entire manuscript. Structure it similarly: Begin with the context and motivation for %the project, a brief description of the method and available data, your findings, and conclusions. Limit yourself to one page!
%\end{abstract}


%----------------------------------------------------------------------------------------
% German ABSTRACT PAGE
%----------------------------------------------------------------------------------------
\begin{extraAbstract}
\addchaptertocentry{\extraabstractname} % Add the abstract to the table of contents

\textbf{Background}. The Swiss Household Panel (SHP) is a nationally representative longitudinal
survey conducted by FORS since 1999, tracking the living conditions of Swiss households. Any
robust analysis of SHP data first requires the construction of a clean, person-year panel
dataset from the confidential SPSS raw files — a non-trivial preparation step that is
implemented reproducibly in this project as part of Practicum 2 of the Data Processing module
at ZHAW.

\textbf{Methods}. Using R (foreign, tidyverse), a person-year panel dataset is built from the SHP
longfiles (SHPLONG\_P\_USER, SHPLONG\_H\_USER) together with the master files SHP\_MP and SHP\_SO.
The full pipeline — extracting the ZIP archive, reading the SPSS files, constructing
variables, merging, filtering (adults only, years in which PP04 was collected), and recoding
SHP missing codes to NA — is documented in a single R Markdown script. The resulting dataset
contains the target variables IDPERS, IDHOUS, YEAR, PP04, BIRTHY, BIRTHYGEN, SEX, CANTON,
EDUCAT, HASKID, NAT, PC19, PP10, NETHHINCPP, PO58, and COMPLETE. On this dataset, we evaluate
descriptive associations between the target variable and the prescribed covariates and test
a self-formulated hypothesis regarding [insert hypothesis].

\textbf{Results}. The processed dataset comprises N = […] person-years across […] waves. The
descriptive analysis shows [insert key findings, e.g. direction and strength of the
association between the target variable and education/income/age]. Plausibility checks
(missing rates, value ranges, distribution across waves) confirm the integrity of the
dataset.

\textbf{Discussion}. The results [support / contradict] the stated hypothesis and are consistent with
[brief contextualisation]. Main limitations concern [e.g. panel attrition, self-reported
measures, non-random missingness]. A natural next step is a model-based analysis (e.g.
fixed-effects regression) on the dataset provided here.

\end{extraAbstract}
